Growth Yield Figures

### 2019-08-16 Growth curves and yields.Rmd
fixed spelling errors

##this data is from non-exponential phase cultures, but the yeld should be fine for the mono-cultures
#Data from PAO1
nonExpPAO1File<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PAO1 growth curves.csv"
nonExpPAO1Data <-read.csv(nonExpPAO1File)
nonExpPAO1Data<- na.omit(nonExpPAO1Data)
nonExpPAO1Data$countsmL<-as.numeric(levels(nonExpPAO1Data$countsmL))[nonExpPAO1Data$countsmL]
nonExpPAO1Data %>% filter(condition=="Mono")->nonExpPAO1DataMono
#Data from PA14
nonExpPA14File<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PA14 growth curves.csv"
nonExpPA14Data <-read.csv(nonExpPA14File)
nonExpPA14Data<- na.omit(nonExpPA14Data)
nonExpPA14Data %>% filter(condition=="Mono")->nonExpPA14DataMono

>>>>

##this data is from non-exponential phase cultures, but the yield should be fine for the mono-cultures
#Data from PAO1
nonExpPAO1File<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PAO1 growth curves.csv"
nonExpPAO1Data <-read.csv(nonExpPAO1File)
nonExpPAO1Data<- na.omit(nonExpPAO1Data)
nonExpPAO1Data$countsmL<-as.numeric(levels(nonExpPAO1Data$countsmL))[nonExpPAO1Data$countsmL]
nonExpPAO1Data %>% filter(condition=="Mono")->nonExpPAO1DataMono
#Data from PA14
nonExpPA14File<-"/Users/jupabago/Documents/Whiteley/PROJECTS/pqsL SCFM2/PA14 growth curves.csv"
nonExpPA14Data <-read.csv(nonExpPA14File)
nonExpPA14Data<- na.omit(nonExpPA14Data)
nonExpPA14Data %>% filter(condition=="Mono")->nonExpPA14DataMono
